On The Impact of Atoms of Confusion in JavaScript Code

### 2021-05-03 1_Introduction.tex
Updates from Overleaf

\begin{figure*}[thb]
\noindent\begin{minipage}{.45\textwidth}  
\begin{lstlisting}[language=JavaScript]
res = properties.reduce((s, b) => {
  b && s++
  return s
}
\end{lstlisting}
\end{minipage}\hfill
\begin{minipage}{.45\textwidth}
\begin{lstlisting}[language=JavaScript]
res = properties.reduce((s, b) => {
  if(b) {
    s = s + 1
  }
  return s
}
\end{lstlisting}
\end{minipage}
\captionof{lstlisting}{Code snippet from \textsc{NervJS/taro} project. Line 2 on the left-hand side of the figure contains two
  atoms of confusion discussed in ~\cite{DBLP:conf/sigsoft/GopsteinIYDZYC17}: \emph{Logic
  as Control Flow} and \emph{Post-increment}. On the right-hand side, we present an alternative implementation without atoms of confusion. We could simplify the code on the left-hand side even more, by using \texttt{filter} and \texttt{length} instead of the \texttt{reduce} recursive pattern (e.g., \texttt{res = properties.filter(p => p).length}).}\label{fig:lst01}
\end{figure*}

@@

  \item A list of additional, JavaScript-specific
    constructs and idioms that might introduce code
    misunderstanding;

    \item A library and infrastructure to mine atoms of confusion using 
    code queries (implemented in the .QL language). This library and 
    infrastructure are freely available and might help researchers and 
    practitioners to automate program analysis at a large scale.

>>>>

\begin{figure*}[thb]
\noindent\begin{minipage}{.45\textwidth}  
\begin{lstlisting}[language=JavaScript]
res = properties.reduce((s, b) => {
  b && s++
  return s
}
\end{lstlisting}
\end{minipage}\hfill
\begin{minipage}{.45\textwidth}
\begin{lstlisting}[language=JavaScript]
res = properties.reduce((s, b) => {
  if(b) {
    s = s + 1
  }
  return s
}
\end{lstlisting}
\end{minipage}
\captionof{lstlisting}{Code snippet from \textsc{NervJS/taro} project. Line 2 on the left-hand side of the figure contains two
  atoms of confusion discussed in ~\cite{DBLP:conf/sigsoft/GopsteinIYDZYC17}: \emph{Logic
  as Control Flow} and \emph{Post-increment}. On the right-hand side, we present an alternative implementation without atoms of confusion. We could simplify the code on the left-hand side even more, by using \texttt{filter} and \texttt{length} instead of the \texttt{reduce} recursive pattern (e.g., \texttt{res = properties.filter(p => p.length})).}\label{fig:lst01}
\end{figure*}

@@

  \item A list of additional JavaScript-specific
    constructs and idioms that might introduce code
    misunderstanding;

    \item A library and infrastructure to mine atoms of confusion using 
    code queries (implemented in the .QL language). This library and 
    infrastructure are publicly available and might help researchers and 
    practitioners to automate program analysis at a large scale.

### 2021-05-03 6_Conclusion.tex
Updates from Overleaf

This paper has reported the results of a mixed-method research effort to better understand the impact of atoms of confusion in JavaScript code. First, we conducted a survey with 140 JavaScript developers. We asked them to predict the output of some code snippets (with and without atoms). We provide evidences that seven atom candidates have a significant impact on program comprehension activities.

Afterwards, we interviewed 15 professional developers. In general, they considered code without atoms of confusion easier to understand and highlighted other JavaScript constructs and idioms that might also introduce misunderstanding. Last but not least, we conducted a mining software repositories study. In particular, we found four atoms of confusion highly used in JavaScript code, i.e., Implicit Predicate, Ternary Operator, Omitted Curly Braces, and Post Increment.

Our efforts have important implications for practice. First, we alert developers to avoid writing JavaScript code with certain atoms of confusion (e.g., Comma Operator, Automatic Semicolon Insertion, Post Increment, and Omitted Curly Braces). Second, our results might help tool developers to create program transformation tools to remove atoms of confusion automaticallu. They might firstly focus, for instance, on the atoms we found to be more confusing and at the same time more common in practice (e.g., Omitted Curly Braces and Post Increment).

As mentioned, the results of the interviews pointed out additional JavaScript constructs and idioms
that might introduce misunderstanding. These include not only nested callbacks and prototype-based
inheritance (which might not have a counterpart version), but also idioms such
as \emph{property access} and \emph{arrow functions}. As future work, we intend to
reproduce our study to validate whether or not these \emph{atom candidates} affect
the understanding of JavaScript code.

>>>>

This paper has reported the results of a mixed-method research effort to better understand the impact of atoms of confusion in JavaScript code. First, we conducted a survey with 140 JavaScript developers. We asked them to predict the output of some code snippets (with and without atoms). We provide evidence that seven atom candidates have a significant impact on program comprehension activities.

Afterwards, we interviewed 15 professional developers. In general, they considered code without atoms of confusion easier to understand and highlighted other JavaScript constructs and idioms that might also introduce misunderstanding. 
%Last, but not least,
Finally, we conducted a mining software repositories study. In particular, we found four atoms of confusion frequently used in JavaScript code, i.e., Implicit Predicate, Ternary Operator, Omitted Curly Braces, and Post Increment.

Our efforts have important implications for practice. First, we alert developers to avoid writing JavaScript code with certain atoms of confusion (e.g., Comma Operator, Automatic Semicolon Insertion, Post Increment, and Omitted Curly Braces). Second, our results might help tool developers to create program transformation tools to remove atoms of confusion automatically. 
%They might firstly focus, for instance, on the atoms we found to be more confusing and at the same time more common in practice (e.g., Omitted Curly Braces and Post Increment).
Promising candidates may be the atoms we found to be most confusing and, at the same time, common in practice (e.g., Omitted Curly Braces and Post Increment).

%As mentioned, the results of the interviews
The results of the interviews pointed out additional JavaScript constructs and idioms
that might introduce misunderstanding. These include not only nested callbacks and prototype-based
inheritance (which might not have a counterpart version), but also idioms such
as \emph{property access} and \emph{arrow functions}. As future work, we intend to
reproduce our study to validate whether or not these \emph{atom candidates} affect
the understanding of JavaScript code.

### 2021-05-03 discussion.tex
additional review (conclusions)
Updates from Overleaf

Our work leads to several implications.
First, we generalize the
work of Gopstein et al.~\cite{DBLP:conf/sigsoft/GopsteinIYDZYC17},
which investigates
the impact of atom candidates on
understanding \clang and \cpplang code. That is,
similarly to their work, the atom candidates
Comma Operator, Post/Pre Increment, Omitted Curly Braces,
Assignment as Value, Implicit Predicate, Logic as
Control Flow, and Ternary Operator make the 
JavaScript code hard to understand. Our results also 
refute the hypothesis that Arithmetic as Logic is an atom of
confusion (i.e., a source of misunderstanding).
In comparison to the previous work, our study
led to some differences in the effect size
of the atom candidates, in comparison to the original
work of Gopstein et al.~\cite{DBLP:conf/sigsoft/GopsteinIYDZYC17}.
Altogether, we answer our first research question
\emph{\rqa}:

\begin{mh}
  {\bf Answer to RQ1:} The first study (survey) give evidence that
  the atom candidates for \clang and \cpplang
  that also exist for JavaScript correspond to
  a source of misunderstanding in
  JavaScript code. 
\end{mh}

The results of the interview study complement the understanding
of atoms of confusion because the participants make
clear the existence of a trade-off between code comprehension
and other quality attributes. For instance, most of the participants
prefer the version of the code with the Ternary Operator,
even though they agree that its uses might contribute to the
misunderstanding of JavaScript code, particularly when novices are maintaining
the codebase. The participants of the interview study also
mentioned other possible sources of misunderstanding in JavaScript,
including the use of prototype-inheritance and nested call-backs (as discussed in Section~\ref{sec:interview-results}). Other JavaScript atom candidates include
Object Destructuring, Array Spread, Object Spread, and Type Conversion.
In summary, the results of the second study (interviews) allow
us to answer the second (\rqb) and third research questions
(\emph{\rqc}).

@@

The result of the third study (mining open source
Java script repositories) give evidence that,
although atoms of confusion compromise program
comprehension, they frequently appear in open
source JavaScript projects. In particular,
{\color{red}six, out of nine atoms considered
  in our study,} appear in more than 50\% of
the projects. To sum up, the third study
allows us to answer the fourth research
question (\emph{\rqd}).

>>>>

Our work leads to several implications.
First, we generalize the
work of Gopstein et al.~\cite{DBLP:conf/sigsoft/GopsteinIYDZYC17},
which investigates
the impact of atom candidates on
understanding \clang and \cpplang code. That is,
similarly to their work, the atom candidates
Comma Operator, Post/Pre Increment, Omitted Curly Braces,
Assignment as Value, Implicit Predicate, Logic as
Control Flow, and Ternary Operator make the 
JavaScript code hard to understand. Our results also 
refute the hypothesis that Arithmetic as Logic is an atom of
confusion (i.e., a source of misunderstanding).
In comparison to the original
work of Gopstein et al.~\cite{DBLP:conf/sigsoft/GopsteinIYDZYC17}, 
our study
led to some differences in the effect size
of the atom candidates.
Altogether, we answer our first research question
\emph{\rqa}:

\begin{mh}
  {\bf Answer to RQ1:} The first study (survey) gives evidence that
  the atom candidates for \clang and \cpplang
  that also exist for JavaScript correspond to
  a source of misunderstanding in
  JavaScript code. 
\end{mh}

The results of the interview study complement the understanding
of atoms of confusion because the participants make
clear the existence of a trade-off between code comprehension
and other quality attributes. For instance, most of the participants
prefer the version of the code with the Ternary Operator,
even though they agree that its use might contribute to the
misunderstanding of JavaScript code, particularly when novices are maintaining
the codebase. The participants of the interview study also
mentioned other possible sources of misunderstanding in JavaScript,
including the use of prototype-inheritance and nested call-backs (as discussed in Section~\ref{sec:interview-results}). Other JavaScript atom candidates include
Object Destructuring, Array Spread, Object Spread, and Type Conversion.
In summary, the results of the second study (interviews) allow
us to answer the second (\rqb) and third research questions
(\emph{\rqc}).

@@

The results of the third study (mining open source
Java script repositories) give evidence that,
although atoms of confusion compromise program
comprehension, they frequently appear in open
source JavaScript projects. In particular,
seven, out of 10 atoms considered
  in our study, appear in more than 50\% of
the projects. 
In summary, the third study
allows us to answer the fourth research
question (\emph{\rqd}).
